---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sui18n

<!-- badges: start -->
<!-- badges: end -->

## Installation

``` r
remotes::install_github("scienceuntangled/sui18n")

```

## Example usage

```{r example}
library(sui18n)

tr <- sui_translator()
tr$set_target("fr")
tr$t("hello")

```

Note that the default translation data is probably of no value to you (unless you have an unhealthy interest in volleyball), and you will probably want to create your own:

```{r example2}
library(tibble)
my_data <- tribble(~key, ~en, ~fr, ~es, ~cat,
                   "greeting", "hello", "bonjour", "hola", "miaow")
tr <- sui_translator(to = "en", csv_path = my_data)

tr$t("greeting")

tr$set_target("cat")
tr$t("greeting")

```

(Or point `csv_path` to a CSV file with similar structure.)

## Using in Shiny apps

In the UI function, call
``` r
sui_js()
```
somewhere to inject the required javascript and

``` r
sui_shinymod_ui(id = "something")
```

to insert the language selector UI element at an appropriate spot in the UI.

Then in your server function:

``` r
my_i18n <- callModule(sui_shinymod_server, id = "something", csv_path = "/path/to/csv")

```

With those pieces in place, you can then use elements in the UI with a `lang_key` attribute:

```r
tags$p(lang_key = "hello")
```

The content of that `p` tag will be automatically populated with the translation of `lang_key` value, and it will change whenever the user changes their selected language. This approach doesn't require any extra reactive code, so it keeps your apps uncluttered. However, it is limited to simple tags (the translated text is inserted into the `element.innerHTML` attribute of the tag). If you need more complex UI structures, you can also use the `my_i18n` object directly. In your UI:

```r
uiOutput("some_element")
```
And in the server:

```r
output$some_element <- renderUI({
    blah <- mi18n$i18n_lang() ## make this expression reactive to the selected language
    tags$p(my_i18n$i18n$t("hello"))
})
```


----

`sui18n` makes use of:

- the [i18njs](https://github.com/roddeh/i18njs) internationalisation library for JS projects. MIT License. Copyright (c) 2013-2018 Simon Rodwell
- flag images from [flag-icons](https://github.com/yammadev/flag-icons). A beautiful svg + png + sass + css collection of 261 flags. MIT License. Copyright (c) 2017 Yefferson

